---
title: "Challenges"
author: "Your Name"
date: "4/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path='figure/')
```

## R Markdown Challenges


> ## Challenge 1
>
> 1. Create a new R Markdown document. Delete all of the R code chunks
> 2. Make a header (H2) using markdown with your name, hint, `##`
> 3. On the next line, make a bullet point and add your department
> 4. Add another bullet point and provide a link to your department or workplace
> 5. After the bullets, write a bit about your research area or what you might like to do in R. 
>
> Convert the document to a webpage.

> ## Challenge 2
>
> To the document you created in Challenge 1, add a code chunk, by selecting <kbd>Insert</kbd> and <kbd>R</kbd>. 
> * Load the ggplot2 package
> * Read the gapminder data
> * Create a plot
> * Change eval=FALSE to eval=TRUE - this tells knit to either run or not run code. 
> * Knit the document

```{r challenge-2, eval=FALSE}
library(______)
library(______)
ggplot(gapminder, aes()) +
  geom_____()
```

> ## Challenge 3
>
> 1. Now create a new R Markdown document, but this time select "Presentation" and "HTML ioslides" option
> 2. Review how the slides are structured. `##` creates a new slide
> 3. Add some of your text from challenge 1 & two to slides. 
> 4. Add an image to a slide. 
> 5. Knit & share your screen with your breakout partners.
>

> ## Challenge 4
> Use chunk options to control the size of a figure and to hide the code.

```{r challenge-4}
plot(faithful)
```


> ## Challenge 5 - A larger example 
> For this challenge we'll use the `index.Rmd` file in the folder you downloaded.
> Open `index.Rmd` and read through the top of the file. On line 50, add different countries in that code chunk. Knit and review the out put. Notice the `index.html` file was created in your file folder. 

> ## Challenge 6 - Sharing your work
> Think about how you can share your work from Challenge 5? You could send the Rmd to a colleague and they could run it. But wouldn't it be cool if you could drag the folder to a website and it would be published? You can! We'll use the Netlify drag and drop <https://app.netlify.com/drop> service to make a website. You need to drag the folder containing your `index.html` to the drag and drop site. Unfortunately, you can't do this inside R Studio. We need to find your folder in Windows File Explorer or Mac Finder. Once found, drag and drop that over. 
> Let's walk through it now. 
> Once you've done this for your folder, paste the link Netlify gives you into the etherpad! You've published your Rmd! You could create an account with Netlify and create a better url. 


>## Challenge 4
>`rticles` package (J. Allaire, Xie, R Foundation, et al. 2020) is designed to simplify the creation of documents that conform to submission standards.
> Install the `rticles` & `TinyTex` packages. Both packages are utility packages, so it's not necessary to use library() to load them. Installing `tinytext` might take a bit. 
> Run the below. It will produce a lot of output. After it completes, look below the output for further instructions. 

```{r rticles, eval=FALSE}
install.packages('rticles')
install.packages('tinytex')
tinytex::install_tinytex()
```

> Now create a new R Markdown documents by selecting <kbd>File</kbd> <kbd>New file</kbd> <kbd>R Markdown...</kbd> and <kbd>From Template</kbd> find Plos Journal Article. Open the new document and examine what is in the template. Add yourself as an author. Change some of the text and <kbd>Knit</kbd>. It should produce a PDF ready for submission. 

